---
title: "Syllabus"
output: html_document
date: "`r Sys.Date()`"
date-format: long
code-fold: false
---

```{r}
#| label: setup
#| include: false
library(googlesheets4)
library(gt)
library(dplyr)
```

This site provides some further information on the objectives and syllabus/organization of the course.

> Course Date: August 25, 2024 (9am-12:30pm, Berlin)

## Course Objectives {.unnumbered}

Attendees of this advanced methods couse will learn how to implement transparent and reproducible workflows across the real-world evidence study lifecycle.

```{mermaid}
%%| label: fig-Objectives
%%| fig-cap: RWE study liefcycle.
flowchart TB
A(Design stage) --> B
B(Analysis execution stage) --> C
C(Reporting stage)
```

-   [**Design stage:**]{.underline} Incorporate **reproducible reporting of key study parameters at a study design and planning stage** using the HARPER protocol

-   [**Analysis stage:**]{.underline} **Version control and share analytic code at the analysis and execution stage** of the study using git and Github

-   [**Reporting stage:**]{.underline} Use **literate programming** by combining narrative language, analytic code and study results for **transparent and reproducible study reporting**

## Syllabus {.unnumbered}

In this practical hands-on course, we introduce resources and tools needed for the transparent and reproducible conduct of RWE studies following **FAIR (Findable, Accessible, Interoperable and Reproducible)** principles.

```{r}
#| label: tbl-timetable
#| tbl-cap: "Detailed course timetable"
#| message: false
#| echo: false

gs4_deauth()
read_sheet(
  ss = Sys.getenv("timetable_url")
  ) |> 
  filter(! Time %in% "Total") |> 
  gt() |> 
  cols_align(align = "left")
```
